Plant Modeling for an Autonomous Vehicle

### 2022-04-04 poster.tex
Poster Updates
I made changes to the Objectives & Contribution section along with the Conclusions & Future Work section. I also made some changes to the title.

\title{Smart Control of 2 Degree of Freedom Helicopters} % Poster title

\author{Glenn Janiak, Ken Vonckx, Advisor: Dr. Suruz Miah} % Author(s)

@@

\begin{alertblock}{Objective and Contribution}
%
\textbf{Objective}
\vskip -0.75cm
\begin{itemize}
    \item Develop a platform allowing mobile devices to control the motion of a group of helicopters
\end{itemize}
%\begin{itemize}
%    \item Develop a platform that allows mobile devices to control helicopters with the least amount of error via an embedded system 
%\end{itemize}
%
\vskip -1cm
\textbf{Contribution}
\vskip -0.75cm
\begin{itemize}
    \item Determine trade-offs between traditional control techniques and machine learning
    %\item Embedded System Implementation
    %\item Mobile Device Control 
    \item Multi-Helicopter Application
\end{itemize}
\vskip -0.75cm
\textbf{Applications}
\vskip -0.75cm
\begin{itemize}
    \item Teleoperation approach to search and rescue 
    \item Aerial turbulence resistance 
\end{itemize}

@@

\begin{alertblock}{Conclusion and Future Work}
\begin{itemize}
    \item Model-based reinforcement learning technique (ADP)  is useful when system model is unknown
   % \item PI controller greatly reduces steady-state error, however increases overshoot and settling time
    \vskip .75cm
    \item Implement PI controller for ADP algorithm
    \item Use digital compass to increase accuracy of orientation and help identify initial position
\end{itemize}

>>>>

\title{Plant Modeling for an Autonomous Vehicle} % Poster title

\author{Nick Nauman, Hannah Grady, Advisor: Dr. Suruz Miah} % Author(s)

@@

\begin{alertblock}{Objective and Contribution}
%
\textbf{Objective}
\vskip -0.75cm
\begin{itemize}
    \item Create models for the subsystems of an autonomous vehicle
\end{itemize}
%\begin{itemize}
%    \item Develop a platform that allows mobile devices to control helicopters with the least amount of error via an embedded system 
%\end{itemize}
%
\vskip -1cm
\textbf{Contribution}
\vskip -0.75cm
\begin{itemize}
	\item Determine if System Identification or Neural Network modeling produces better models 
	\item Non-linearity modeling
%    \item Determine trade-offs between traditional control techniques and machine learning
    %\item Embedded System Implementation
    %\item Mobile Device Control 
    %\item Multi-Helicopter Application
\end{itemize}
\vskip -0.75cm
\textbf{Applications}
\vskip -0.75cm
\begin{itemize}
	\item Use in testing to help develop more accurate vehicle controllers
	\item Create a guide for modeling future vehicle subsystems
%    \item Teleoperation approach to search and rescue 
%    \item Aerial turbulence resistance 
\end{itemize}

@@

\begin{alertblock}{Conclusion and Future Work}
\begin{itemize}
    \item Using Neural Networks produced more accurate models than System Identification 
   % \item PI controller greatly reduces steady-state error, however increases overshoot and settling time
    \vskip .75cm
    \item Test models using Hardware-in-the-Loop
    \item Create new vehicle controllers
\end{itemize}
